Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-20 p2/axiom-proof.tex
Review
Formatting

We can proceed in the same fashion if $\czwmv\aFS$ is not broken, but
$(\czwmv\cc\cxynv)\aFS$ is.
\end{proof}

@@

\begin{proof}
It is easy to see that where both $\cxynv\cc \czwnv$ and $\cxwnv$ are defined
(they do not break the filesystem), they are equivalent.
What remains to show is that they break the same set of filesystems.
If $(\cxynv\cc \czwnv)\aFS$ is not broken, then we know that neither of
$\FS$, $\fsreplacement{\FS}{n}{y}$ or $\fsreplacement{\FS}{n}{w}$ is broken,
and therefore $\cxwnv$ does not break $\FS$.
Conversely, if $\cxwnv$ does not break $\FS$, then 
we know that $\FS$ and $\fsreplacement{\FS}{n}{w}$ are not broken.
Also, as
either $[x]\neq[\empt]$ or $[w]\neq[\empt]$,
there must be a directory at $\FS(\parentf{n})$,
and so $\fsreplacement{\FS}{n}{y}$ cannot be broken, either,
as any value is permissible at $n$.
This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.

We note that if $\cxwnv$ is an assertion command, then it extends $\cxynv\cc\czwnv$
instead of being equivalent to it.
\end{proof}

@@

\begin{proof}
The two assertion commands $\cdda{n}$ and $\cbba{n}$ either
breaks a filesystem, or leaves it in the same state.
\end{proof}

>>>>

\begin{sloppypar}
We can proceed in the same fashion if $\czwmv\aFS$ is not broken, but
$(\czwmv\cc\cxynv)\aFS$ is.
\end{sloppypar}
\end{proof}

@@

\begin{proof}
It is easy to see that where both $\cxynv\cc \czwnv$ and $\cxwnv$ are defined
(they do not break the filesystem), they are equivalent.
What remains to show is that they break the same set of filesystems.
If $(\cxynv\cc \czwnv)\aFS$ is not broken, then we know that neither of
$\FS$, $\fsreplacement{\FS}{n}{y}$ or $\fsreplacement{\FS}{n}{w}$ is broken,
and therefore $\cxwnv$ does not break $\FS$.
Conversely, if $\cxwnv$ does not break $\FS$, then 
we know that $\FS$ and $\fsreplacement{\FS}{n}{w}$ are not broken.
Also, as
either $[x]\neq[\empt]$ or $[w]\neq[\empt]$,
there must be a directory at $\FS(\parentf{n})$,
and so $\fsreplacement{\FS}{n}{y}$ cannot be broken, either,
as any value is permissible at $n$.
This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.
We note that if $\cxwnv$ is an assertion command, then it extends $\cxynv\cc\czwnv$
instead of being equivalent to it.
\end{proof}

@@

\begin{proof}
The two assertion commands $\cdda{n}$ and $\cbba{n}$ either
break a filesystem, or leave it in the same state.
\end{proof}
